---
title: "Task4"
author: "Kirill Tumanov"
date: "15 11 2019"
output: 
   html_document:
    theme: journal
    highlight: haddock
    toc: true
    toc_float: false
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(scales)
library(dplyr)
library(lubridate)
library(readr)
library(forecast)
```

#Download data
```{r}
storedata <- read_csv("C:/Users/Asus/Downloads/storedata.csv")
storedata <- storedata %>%
  mutate(Order_Date = as.Date(Order_Date),
         year = lubridate::year(Order_Date),
         month = lubridate::month(Order_Date))
```

#Task1
For the last 3 months of 2017, calculate the total Sales by month, for Region 1 and Region 9 in the Customer_Segment, Corporate and Consumer. This output is Table 1.
```{r}
Table1 <- storedata %>%
  filter(year==2017, month>=10) %>%
  filter(Region == "Region 1" | Region == "Region 9") %>%
  filter(Customer_Segment == "Corporate" | Customer_Segment == "Consumer") %>%
  group_by(month, Region, Customer_Segment) %>%
  summarise(TotalSales = sum(Sales))
view(Table1)
```

#Task2
Make a plot of the monthly total Sales in Region 1 and Region 13 in 2015, 2016 and 2017. This output is Figure 1.
```{r}
Figure1 <- storedata %>%
  filter(year<=2017&year>=2015) %>%
  filter (Region == "Region 1" | Region == "Region 13") %>%
  group_by(year, month, Region) %>%
  summarise(TotalSales = sum(Sales)) %>%
  mutate(date = as.Date(lubridate::ymd(paste(year,month,01))))

Figure1 %>%
  ggplot(aes(x = date, y = TotalSales, color = Region)) +
  geom_line() +
    labs(x = "Date", y = "Total Sales", title = "The monthly total Sales in Region 1 and Region 13 in 2015, 2016 and 2017") + scale_x_date(breaks = date_breaks("months"), labels = date_format("%b-%y")) +  theme(axis.text.x = element_text(angle=50))
```

#Task3
In Figure 1, identify the months where the total Sales in Region 13 is greater than the total Sales in Region 1. This output is Table 2.
```{r}
data01 <- Figure1 %>% filter(Region == "Region 1")
data02 <- Figure1 %>% filter(Region == "Region 13")
Table2 <- full_join(data01, data02, by="date") %>%
  mutate(diff = (TotalSales.y - TotalSales.x) > 0) %>% filter(diff > 0) %>%
  select(date, diff)

names(Table2) <- c("year","month","Date","Total Sales: Region 13 > 1")
Table2 <- Table2[,c("Date","Total Sales: Region 13 > 1")]

view(Table2)
```

#Task4
Find average Profit per Customer_Segment and Product_Category in 2017, for all regions except Region 3, 5 and 8. What segment produced the highest average profit? This output is Table 3.
```{r}
Table3 <- storedata[storedata$Order_Date >= "2017-01-01" & storedata$Order_Date <= "2017-12-31",] %>%
  filter(year==2017) %>%
  filter(Region == c("Region 1", "Region 2", "Region 4", "Region 6", "Region 7", "Region 9", "Region 10", "Region 11", "Region 12", "Region 13")) %>%
  select(Profit, Customer_Segment, Product_Category, Region) %>%
group_by(Region, Customer_Segment, Product_Category) %>% 
  summarise(Average_profit = mean(Profit)) %>%
  arrange(-`Average_profit`)

view(Table3)
```
The highest average profit was received by Small Business in Region 9. This number was 4801.
Product category was Furniture.

#Task5
Estimate a SARIMA model on the aggregated monthly Order_Quantity in the Customer_Segment; Small Business and Product_Category; Office Supplies. The SARIMA model contains the following parameters:
p - AR order, 
d - difference order, 
q - MA order, 
P - SAR order, 
D - seasonal difference, 
Q - SMA order, 
S - seasonal period (12 months in these data)
```{r}
##Preparing Data
sarmodel <- storedata[storedata$Customer_Segment=="Small Business"& storedata$Product_Category=="Office Supplies",]
sarmodel <- sarmodel %>% 
   group_by(year, month) %>%
  summarise(sum_ord_quant = sum(Order_Quantity))
sar_now <- sarmodel %>%
   filter(year<=2016&year>=2014)
sar_future <- sarmodel %>%
   filter(year==2017)

##What is Arima? Testing
###Arima14-16
tsdata14_16 <- ts(sar_now$sum_ord_quant, frequency = 12, start = c(2014, 1),end=c(2016, 12))
plot(tsdata14_16)
autoarima01 <- auto.arima(tsdata14_16)
forecast01 <- forecast(autoarima01, h=12)
plot(forecast01)

p <- (0:4)
d <- (0:1)
q <- (0:4)
P <- (0:4)
D <- (0:1)
Q <- (0:4)

###Arima17
tsdata17 <- ts(sar_future$sum_ord_quant, frequency = 12, start=c(2017, 1), end=c(2017, 12))
plot(tsdata17)
autoarima02 <- auto.arima(tsdata17)
forecast02 <- forecast(autoarima02, h=12)
plot(forecast02)
```

#Plots
```{r}
#2014-2016
fit01 <- Arima(tsdata14_16, order=c(0,1,1), seasonal=c(1,1,1))
checkresiduals(fit01)
fit01 %>% forecast(h=12) %>% autoplot(xlab="Date", ylab="Order Quantity",
    main="Order Quantity 2014-2016")

#The forecast for 2017
Figure2 <- Arima(tsdata17, order=c(1,1,0), seasonal=c(0,0,1))
checkresiduals(Figure2)
Figure2 %>% forecast(h=12) %>% autoplot(xlab="Date", ylab="Order Quantity",
    main="The forecast of order quantity for 2017 ")
```

